### 2015-05-13 intro.tex
update in intro

We then show that by exploiting the race-freedom guarantees that our symbolic analysis provides, we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a state-of-the-art bug-finder that is used by Microsoft to analyze device drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers available in the 4.0 Linux kernel distribution.

>>>>

We then show that by exploiting the race-freedom guarantees that our symbolic analysis provides, we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a state-of-the-art bug-finder that is used by Microsoft to analyze device drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers available in the 4.0 Linux kernel distribution, and show that we can achieve speedups in the range of 1.5--10$\times$ in most of our benchmarks, while we managed to achieve a speedup greater than 10$\times$ and 20$\times$ in two cases.
